\phantomsection
\pagenumbering{Roman}
\addcontentsline{toc}{chapter}{摘\hspace{1em}要}

\begin{cnabstract}{特定风格；LoRA技术；视频生成；扩散模型；参数高效微调}
随着生成式人工智能的发展，如何以较低成本生成具有特定艺术风格且质量稳定的视频，已经成为当前研究中的一个重要问题。传统视频生成模型往往依赖较高算力和全参数微调，训练开销大，同时在保持目标风格的过程中还容易破坏时序一致性。针对这一问题，本文提出了一种基于LoRA（Low-Rank Adaptation）技术的特定风格视频生成研究框架，尝试在有限算力和有限样本条件下，探索一条兼顾风格表达与工程可行性的技术路线。

本文首先梳理了扩散模型与潜空间生成技术的基本原理，分析了LoRA参数高效微调方法在特定风格适配中的适用性。在数据准备阶段，通过对目标动画风格图像进行规范化预处理与自动标注，构建了包含810张样本的吉卜力动画风格数据集。在模型训练阶段，本文以Stable Diffusion 1.5为核心底模设计LoRA注入策略，并比较了不同底模（StorybookRedmond、Counterfeit-V3.0）在相近训练强度下的表现差异。实验结果表明，加载LoRA适配器后，模型在颜色分布、线条强度和场景组织上均产生了稳定且可观测的风格偏移；具有较强视觉先验的底模能够进一步增强风格迁移强度，但同时也需要在风格纯度与内容保真之间做出权衡。

在视频验证阶段，本文构建了递推式短视频生成原型，并引入无参考时序一致性评估指标。量化分析表明，加载风格LoRA后，视频的相邻帧像素平均绝对差（MAD）和边缘变化平均绝对差（MED）均有所下降，说明图像阶段获得的风格能力能够在一定程度上迁移到连续帧中。针对实验中暴露出的亮度稳定性（LS）波动问题，本文进一步分析了其形成原因，并提出了后续引入显式运动模块与结构控制技术的改进方向。本文的研究为独立创作者和中小团队开展个性化视频内容生产提供了可复用的技术参考。
\end{cnabstract}

\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}

\begin{enabstract}{Specific Style; LoRA Technology; Video Generation; Diffusion Models; Parameter-Efficient Fine-Tuning}
With the development of Artificial Intelligence Generated Content (AIGC), low-cost generation of high-quality videos with specific artistic styles has become an important research topic. Traditional video generation models usually depend on substantial computational resources and full-parameter fine-tuning, while still struggling to maintain both stylistic consistency and temporal stability. To address this issue, this thesis proposes a research framework for specific-style video generation based on LoRA (Low-Rank Adaptation), aiming to explore a technical route that balances style expression and engineering feasibility under limited computational resources and sample sizes.

The thesis first reviews the basic principles of Diffusion Models and Latent Diffusion frameworks, and analyzes the suitability of LoRA parameter-efficient fine-tuning for specific style adaptation. In the data preparation stage, a stylized dataset containing 810 samples was built through standardized preprocessing and automated captioning of target animation images. At the model training stage, Stable Diffusion 1.5 was adopted as the core base model, a LoRA injection strategy was designed, and the performance of different base models (StorybookRedmond and Counterfeit-V3.0) was compared under similar training intensities. Experimental results show that loading LoRA adapters leads to stable and observable style shifts in color distribution, line intensity, and scene organization. Base models with stronger visual priors can further strengthen style transfer, but they also require a trade-off between style purity and content fidelity.

In the video validation stage, a recursive short-video generation prototype was constructed, and no-reference temporal consistency metrics were introduced. Quantitative analysis indicates that after loading the style LoRA, both the Mean Absolute Difference (MAD) and the Mean Edge Difference (MED) of adjacent frames decreased, showing that the learned style capability can be transferred to continuous frames to a certain extent. To address the Brightness Standard Deviation (LS) fluctuations observed in the experiments, this thesis further analyzes the underlying causes and proposes future improvements involving explicit motion modules and structural control techniques. The study provides a reusable technical reference for independent creators and small teams engaged in personalized video content production.
\end{enabstract}
